Formalization, Mechanization and Automation of G\"{o}del's Proof of God's Existence\thanks{This work has been supported by the German Research Foundation under grant BE2501/9-1.}

### 2013-08-20 Abstract/GodProof-Abstract.tex
Fix typo
Improve natural language statements of axioms and definitions.
Justifications for improvements:

A2 - "contains" presupposes a set-theoretic interpretration for properties

A4 - it is intuitively strange to talk about properties "being" (existing), even though technically that's what we do with Henkin semantics. I belive my reformulation is less strange in this respect.

Natural language text is more "natural" when it doesn't contain logical variables and it can also be more easily appreciated by readers who are not formal logicians.

\allowdisplaybreaks[1] 
\begin{description}
\item[A1] Either the property or its negation is positive, but not
  both:  \hfill 
  $\all \phi. [P(\neg \phi) \biimp \neg P(\phi)]$
\item[A2] A property is positive if it necessarily  contains a
  positive property:  \\ \phantom{b} \hfill 
  $\all \phi. \all \psi.[(P(\phi) \wedge \nec \all x.[\phi(x)
  \imp \psi(x)]) \imp P(\psi)]$ 
\item[T1] Positive properties are possibly exemplified. \hfill $\all \varphi. [P(\varphi) \imp \pos \ex x.\varphi(x)]$
\item[D1] x is God-like if it possesses all positive properties: \hfill
  $G(x) \biimp \forall \phi. [P(\phi) \to \phi(x)]$
\item[A3]  The property of being God-like is positive: \hfill   $P(G)$
\item[C\phantom{1}] Possibly, God exists: \hfill $\pos \ex x. G(x)$
\item[A4]  Being a positive property is logical, hence,
  necessary: \hfill 
  $\all \phi.[P(\phi) \to \Box \; P(\phi)]$
\item[D2] $\phi$ is the essence of $x$ iff $x$ has $\phi$ and this
  property is necessarily minimal.:\\
  \phantom{b} \hfill $\ess{\phi}{x} \biimp \phi(x) \wedge \all
  \psi. (\psi(x) \imp \nec \all y. (\phi(y) \imp \psi(y)))$
\item[T2]  The property of being God-like is an essence of any
  God-like being: \hfill $\all y.[G(y) \imp \ess{G}{y}]$ 
\item[D3] $\NE(x)$ means that $x$ necessarily exists if it has an
  essential property: \\
  \phantom{b} \hfill $\NE(x) \biimp \all \phi.[\ess{\phi}{x} \imp \nec \ex x.\phi(x)]$
\item[A5] Necessary existence is a positive property: \hfill $P(\NE)$
\item[T3] Necessarily, God exists: \hfill $\nec \ex x. G(x)$ 
\end{description}

@@

In our ongoing computer-assisted study of G\"odel's proof we have
obtained the following results:
\begin{itemize}
\item Logic S5 is not needed for obtaining the results, logic KB is
  sufficient.
\item For proving theorem T1, only the left to right direction of
  axiom A1 is needed. However, the backward direction of A1 is
  required for showing T2.
\item The first conjunct $\phi(x)$ in D2, introduced by Scott, seems important; without it the set of axioms and definitions becomesx inconsistent.
\end{itemize}

>>>>

\allowdisplaybreaks[1] 
\begin{description}
\item[A1] Either the property or its negation is positive, but not
  both:  \hfill 
  $\all \phi. [P(\neg \phi) \biimp \neg P(\phi)]$
\item[A2] A property is positive if it is necessarily implied by a
  positive property:  \\ \phantom{b} \hfill 
  $\all \phi. \all \psi.[(P(\phi) \wedge \nec \all x.[\phi(x)
  \imp \psi(x)]) \imp P(\psi)]$ 
\item[T1] Positive properties are possibly exemplified. \hfill $\all \varphi. [P(\varphi) \imp \pos \ex x.\varphi(x)]$
\item[D1] A God-like being possesses all positive properties: \hfill
  $G(x) \biimp \forall \phi. [P(\phi) \to \phi(x)]$
\item[A3]  The property of being God-like is positive: \hfill   $P(G)$
\item[C\phantom{1}] Possibly, God exists: \hfill $\pos \ex x. G(x)$
\item[A4]  Positive properties are necessarily positive: \hfill 
  $\all \phi.[P(\phi) \to \Box \; P(\phi)]$
\item[D2] An essence of an individual is a property possessed by it and necessarily implying any of its properties:\\
  \phantom{b} \hfill $\ess{\phi}{x} \biimp \phi(x) \wedge \all
  \psi. (\psi(x) \imp \nec \all y. (\phi(y) \imp \psi(y)))$
\item[T2]  Being God-like is an essence of any
  God-like being: \hfill $\all y.[G(y) \imp \ess{G}{y}]$ 
\item[D3] Necessary existance of an individual is the necessary exemplification of all its essences: \\
  \phantom{b} \hfill $\NE(x) \biimp \all \phi.[\ess{\phi}{x} \imp \nec \ex x.\phi(x)]$
\item[A5] Necessary existence is a positive property: \hfill $P(\NE)$
\item[T3] Necessarily, God exists: \hfill $\nec \ex x. G(x)$ 
\end{description}

@@

In our ongoing computer-assisted study of G\"odel's proof we have
obtained the following results:
\begin{itemize}
\item Logic S5 is not needed for obtaining the results, logic KB is
  sufficient.
\item For proving theorem T1, only the left to right direction of
  axiom A1 is needed. However, the backward direction of A1 is
  required for showing T2.
\item The first conjunct $\phi(x)$ in D2, introduced by Scott, is important; without it the set of axioms and definitions becomes inconsistent.
\end{itemize}
